\documentclass[a4paper,12pt]{article}
\usepackage{TLCresume}
\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line

%====================
% EXPERIENCE A
%====================

\vspace*{10pt}
\subsection{{CVML Intern }\hfill 05/23 - 08/23}
\subtext{Kuartis \hfill Ankara}
\begin{zitemize}
    \item Created ROS2 tutorials for upcoming interns.
    \item Conducted literature research on LIDAR and RADAR point cloud data processing techniques, evaluating metrics and overall performance for comparison. Implemented these techniques and presented findings.
    \item Implemented the paper "Exploiting Temporal Context for Tiny Object Detection" using PyTorch.
    \item Conducted literature research on road segmentation in satellite images.
    \item Delivered a presentation on Liquid Neural Networks and Neural Circuit Policies.
\end{zitemize}


%==================== 
% EXPERIENCE B 
%==================== 
\vspace*{6pt}
\subsection{{Undergrad Research Intern }\hfill 04/22 - 01/23}
\subtext{TOBB ETU Kasirga Research Group \hfill Ankara}
\begin{zitemize}
\item Designed a UART peripheral module for Teknofest 2022 processor. 
\item Read papers on computer architecture and gained experience on both evaluating and presenting them.
\item Worked on in-house cycle level accurate Risc-V processor simulation using modern C++.
\item Worked on parallel programming paradigms and API's OpenMP, CUDA etc.
\item Worked as teaching assistant on Digital Design and Computer Architecture courses.

\end{zitemize}

%==================== 
% EXPERIENCE C
%==================== 
\vspace*{6pt}
\subsection{{Engineering Intern }\hfill 09/21 - 01/22}
\subtext{HAVELSAN \hfill Ankara}
\begin{zitemize}
\item Worked on a VTOL UAV's inner dynamics, test procedures and project development parts. Participated in field tests and assembling processes.
\item Developed an object detection system with a stereo depth camera and collected the depth information of the scene .
\item Implemented and worked on convolutional neural networks, created my own custom dataset and used transfer learning on a pre-trained network with my dataset.
\item Worked on robot operating frameworks, Linux operating systems, and developed a basic understanding on development processes.

\end{zitemize}

\end{document}